---
title: "IMABC Calibration Report"
author: "Pedro Nascimento de Lima"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  versions: !r c("2.6")                  # model versios to include
  scenarios: !r c(1,2,3)                    # scenarios to include
  rounds: !r c("07") # c("01","03","05", "06")   # run "rounds" to include
  filter_experiments: !r FALSE             # whether or not to filter experiments
  experiments_to_select: !r c("v2.6_1.07", "v2.6_4.04") # which specific experiments to include in the report.
#output:
#  md_document:
#    variant: markdown_github
#    toc: true
#    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width = 10, fig.height = 6)
# Change your base_path accordingly:
#base_path = "/lcrc/project/EMEWS/plima/crcspin-imabc/"
#setwd(base_path)
library(dplyr)
library(ggplot2)
library(tidyr)
library(patchwork)
library(ggforce)
library(here)
library(randplot)
library(future)
library(furrr)
# install with remotes::install_github("https://github.com/RANDCorporation/randplot")

# Using here because of R markdown.
source(paste0(here::here(),"/R/calibration_report_functions.R"))
source(paste0(here::here(),"/R/user_fns/range_check.R"))
source(paste0(here::here(),"/R/scenarios.R"))
```

## Intro

This file is used to generate plots and summary statistics for a calibration campaign using IMABC. This code is most useful to compare a few different experiments (either different iterations or separate calibrations).

## Reading Experiments

Here we read the experiment results:

```{r read_experiments}

# anl path: "/lcrc/project/EMEWS/plima/crcspin-imabc/"
results_path = "/lcrc/project/EMEWS/plima/crcspin-imabc/experiments/"
#results_path = "/Users/plima/Documents/OneDrive/crcspin-imabc/experiments/"

# You can select different experiments under the ./experiment folders. 
# Here I select the most recent run for each of the scenarios. This may also be useful to compare iterations.
version = params$versions
scenario = params$scenarios
round = params$rounds

# Creating a table of experiments:
experiments_df = expand_grid(version, scenario, round) %>%
  mutate(experiment = paste0(version, ".", scenario, ".", round))

if(params$filter_experiments){
  experiments_df = experiments_df %>%
    dplyr::filter(experiment %in% params$experiments_to_select)
}


# Comparing Different Experiments:
# Progression:
experiments = experiments_df$experiment 

#experiments = c("v2.5_1.03.05", "v2.6_1.01")
experiment_names = experiments
# experiments = c("v2.5_1.03.05", "v2.5_2.03.04", "v2.5_3.03.05", "v2.5_4.03.05", "v2.6_1.01")
# experiment_names = c("a:20, s:high", "a:15, s:high", "a:10, s:high", "a:20, s:med", "v2.6_1")


# Read each file from all the experiment folders:
distances = get_experiments_results(file_name = "SimulatedDistances", results_path = results_path, experiments = experiments, experiment_names = experiment_names)
parameters = get_experiments_results(file_name = "SimulatedParameters", results_path = results_path, experiments = experiments, experiment_names = experiment_names)
targets = get_experiments_results(file_name = "SimulatedTargets", results_path = results_path, experiments = experiments, experiment_names = experiment_names)
current_targets = get_experiments_results(file_name = "CurrentTargets", results_path = results_path, experiments = experiments, experiment_names = experiment_names)
good_params = get_experiments_results(file_name = "Good_SimulatedParameters", results_path = results_path, experiments = experiments, experiment_names = experiment_names) %>%
  dplyr::left_join(experiments_df, by = "experiment")
good_targets = get_experiments_results(file_name = "Good_SimulatedTargets", results_path = results_path, experiments = experiments, experiment_names = experiment_names)

# Joining some of these files:
distance_parameters = distances %>% 
  left_join(parameters, by = c("experiment", "iter", "draw", "step"))

distance_parameters$non_nas = 42 - apply(distance_parameters, MARGIN = 1, function(x) sum(is.na(x)))

good_targets_params = good_targets %>%
  left_join(good_params, by = c("experiment", "iter", "draw", "step"))

# Vector of parameter and target names:
param_names = read.csv(file = "./data/inputs/priors_v2.6.1.csv", stringsAsFactors = F) %>%
  filter(dist_base_name != "fixed") %>%
  .$parameter_name
  
target_names = colnames(targets)[4:length(targets)-1]

# Obtain target names and groups and 
orig_targets = read.csv(file = "./data/inputs/targets_v2.6.csv", stringsAsFactors = F)
# removes everything that comes before the first _
orig_targets$short_names = sub(".+?_", "", orig_targets$target_names)

# Update the current_targets object with those names:
current_targets$target_group = orig_targets$target_group
current_targets$short_names = orig_targets$short_names

# This is useful for plotting target values:
long_good_targets = good_targets %>%
  tidyr::pivot_longer(cols = all_of(target_names) ,names_to = "target_names") %>%
  left_join(current_targets %>% select(target_names, target_group, short_names), by = "target_names")

s_colors = randplot::RandCatPal[1:length(unique(good_params$experiment))]

# This is setting the default themes and colors. Will need to change if # of scenarios is not 4:
ggplot <- function(...) ggplot2::ggplot(...) + scale_color_manual(values = s_colors) + scale_fill_manual(values = s_colors) + theme_bw() + theme(legend.position = "top")

# Write summary files:
write.csv(x = current_targets, "./analysis/current_targets.csv")

```

Calculate additional results for each good parameter:

```{r}

# system.time({
#   purrr::pmap_dfr(.l = good_params, .f = interpretable_param_outcomes, scenarios_list = scenarios_list)  
# })
# without registering the parallel backend:
plan(multisession, workers = 30) # use multisession for windows (PSOK)
system.time({
  additional_results = furrr::future_pmap_dfr(.l = good_params, .f = interpretable_param_outcomes, scenarios_list = scenarios_list)  
})
plan(sequential)



```

This table defines the experiments included in the report:

```{r}
experiments_df
```

And this list includes the inputs used within each scenario:

```{r}
scenarios_list
```


## Number of good parameters per experiment:

```{r}
good_params %>%
  group_by(experiment) %>%
  summarise(max_iter = max(iter),
            n_good = n())
```


## Number of good parameters per iteration and experiment:

```{r}
good_params %>%
  group_by(experiment, iter) %>%
  summarise(n_good = n()) %>%
  tidyr::pivot_wider(names_from = "experiment", values_from = "n_good")
```

## Density Plots for parameters

```{r density-plots, fig.height=5, fig.width=5}

param_names = c(param_names, names(additional_results)[40:65])

# Density plot for all parameters:
for(param_x in param_names){
  print(density_plot_by_experiment(data = additional_results, param_x))
}
```

## Parameter Pairs plot

This plot is more useful with a handful of parameters each time:

Risk:

```{r pairs1}
pairs_plot(good_params, param_names[grep("ar\\.", param_names)])


# GGally::ggpairs(data = good_params,columns = param_names[1:7], 
#                 mapping = aes(color = experiment),
#                 upper = list(continuous = "density", combo = "box_no_facet"),
#                 lower = list(continuous = "points", combo = "dot_no_facet"))

```

Cum Risk and Exp. Prevalence:

```{r}
pairs_plot(additional_results, param_names[grep("cum.risk.", param_names)])
pairs_plot(additional_results, param_names[grep("prev.", param_names)])
pairs_plot(additional_results, param_names[c(grep("mean_time10", param_names), grep("pct_10mm", param_names))])
pairs_plot(additional_results, param_names[grep("m.size.at", param_names)])
pairs_plot(additional_results, param_names[c(grep("mst_", param_names), grep("medst", param_names))])
```

Growth:

```{r pairs2}
pairs_plot(good_params, param_names[grep("growth\\.", param_names)])
```

Trans:

```{r pairs3}
pairs_plot(good_params, param_names[grep("trans\\.prob\\.", param_names)])
```

Mst:

```{r pairs4}
pairs_plot(good_params, param_names[grep("mst\\.", param_names)])
```

## Targets and Parameters:

One can also use the same pairs plot on the targets and parameters:

```{r pairs5}
pairs_plot(data = good_targets_params,variables = c("ar.mean", "Lieberman_pct_crc_10plusmm", "Church_pct_crc_10plusmm"))
```

## Targets

This plot is clearly trying to show too much in one figure. The grey area are the final target bounds.

```{r}

# Use the plot target function to plot all targets:
all_targets_but_seer_plot = plot_targets(targets_def = orig_targets, current_targets = current_targets, long_good_targets = long_good_targets,  target_groups =  c("Pickhardt", "Church", "Corley", "Lieberman", "UKFSS"))

seer_targets_plot = plot_targets(targets_def = orig_targets, current_targets = current_targets, long_good_targets = long_good_targets, target_groups =  c("SEER"))

all_targets_but_seer_plot
seer_targets_plot

```


```{r eval=FALSE, include=FALSE}

# Use the plot target function to plot all targets:
all_targets_but_seer_plot / seer_targets_plot + plot_layout(guides = "collect") & theme(legend.position = 'bottom')

```


